The French Covid-19 vaccination policy did not solve vaccination inequities: a nationwide longitudinal study on 64.5 million individuals

### 2022-07-04 ms/figs.Rmd
format supp table

>>>>

write.csv(tmp.perm, file = "../ms/SuppTable_ORpermutations99.csv", row.names = FALSE)

# Combine the two in a single table
#  New column to store the result
tmp$significant <- NA
tmp$OR_permutation <- NA

for(i in seq_len(nrow(tmp))){
  # Sort CI values
  tmp[i, c("OR CI min", "OR CI max")] <- sort(tmp[i, c("OR CI min", "OR CI max")])
  # Test significativity
  ORabs <- max(tmp[i, "OR"], 1/tmp[i, "OR"])
  ORref <- tmp.perm[tmp.perm$date == tmp[i, "date"], "q99"]
  if(ORabs > ORref) tmp[i, "significant"] <- TRUE
  if(ORabs < ORref) tmp[i, "significant"] <- FALSE
  tmp[i, "OR_permutation"] <- ORref
}

# Round the values
dgt <- 3
tmp$OR <- round(tmp$OR, digits = dgt)
tmp$`OR CI min` <- round(tmp$`OR CI min`, digits = dgt)
tmp$`OR CI max` <- round(tmp$`OR CI max`, digits = dgt)
